The aims of science and an open science controversy at USEPA

### 2024-05-16 paper/methods.qmd
initial work on paper
date and length plots

After scraping, our corpus included the text of 22,390 comments and attachments for 20,787 distinct comments.  *[try reruning scraper sometime]*  We refer to this collection of comments and attachments as the *ST corpus*.  By number of attachments, the median document had no attachments and the maximum number of attachments was 17.

@@

[A1] began to develop a strategy for sampling from across this principal component.  Drawing the most extreme documents from either end resulted in a large number of nearly identical "form letter" comments, most likely collected by advocacy organizations using online forms.  Using phrases that appeared in these comments and simple text matching, [A1] excluded 8,875 from three different forms from the manual coding sample.  After these exclusions, drawing the most extreme 200 documents (including ties) from each end resulted in *[actual numbers, pre-fixing html issue]* 214 from the "bottom" (apparently supportive) and 201 from the "top" (apparently opposed).  Then a simple random sample of 400 comments was drawn from the remaining 6,561 comments (15.8k that contained one or more bigram, less the 8.9k from identified form letters and the 415 from the extremes).  The resulting sample contained 814 comments.^[While manual coding was underway, [A1] prepared draft code for the imputation and analysis steps described below.  This revealed an error in the part-of-speech tagging:  spaCy assumes it is working with plain, pre-cleaned text, but the comment text can contain HTML, especially `<br>` tags.  After fixing this error, the bigram subset was slightly smaller, and some documents used in manual coding were no longer in the bigram subset.  This is why the data used for imputation and analysis is slightly smaller than reported here.]

@@

\[ pmi(x, y) = \log \frac{p(x, y)}{p(x) p(y) }\]

>>>>

After scraping, our corpus included the text of 22,390 comments and attachments for 20,787 distinct comments.  We refer to this collection of comments and attachments as the *ST corpus*.  By number of attachments, the median document had no attachments and the maximum number of attachments was 17.

Comments were primarily submitted during two public comment periods, one following the publication of the Notice of Proposed Rulemaking (NPR) on *[date]* and the second in response to the Revised Notice of Proposed Rulemaking (RNPR) on *[date]*.  Comments varied in length dramatically: a few handwritten postcards could not be parsed by OCR and were counted as being 0 words in length, and the longest comment (including the comment text and all attachment text) was 467,917 words long. The median comment was 236 words long, and 95% of comments were 495 words long or less. See figure @fig-date-ecdf.

![(a) Count of submissions, aggregated by week; note the y-axis uses a square root scale. (b) Cumulative frequency of comment lengths, by number of words.](../out/04_date_ecdf.png){#fig-date-ecdf}

@@

[A1] began to develop a strategy for sampling from across this principal component.  Drawing the most extreme documents from either end resulted in a large number of nearly identical "form letter" comments, most likely collected by advocacy organizations using online forms.  Using phrases that appeared in these comments and simple text matching, [A1] excluded 8,875 comments matching three different forms from the manual coding sample.  After these exclusions, drawing the most extreme 200 documents (including ties) from each end resulted in *[actual numbers, pre-fixing html issue]* 214 from the "bottom" (apparently supportive) and 201 from the "top" (apparently opposed).  Then a simple random sample of 400 comments was drawn from the remaining 6,561 comments (15.8k that contained one or more bigram, less the 8.9k from identified form letters and the 415 from the extremes).  The resulting sample contained 814 comments.^[While manual coding was underway, [A1] prepared draft code for the imputation and analysis steps described below.  This revealed an error in the part-of-speech tagging:  spaCy assumes it is working with plain, pre-cleaned text, but the comment text can contain HTML, especially `<br>` tags.  After fixing this error, the bigram subset was slightly smaller, and some documents used in manual coding were no longer in the bigram subset.  This is why the data used for imputation and analysis is slightly smaller than reported here.]

@@

$$ pmi(x, y) = \log \frac{p(x, y)}{p(x) p(y) }$$
